A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries

### 2022-09-17 src/docs_04-01-22-update/04-01-22-update.Rmd
update upload

```{r echo=FALSE}
knitr::include_graphics("depends/3-rank-comparison.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/continental-map.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/within-between-country-variation.pdf")
```

```{r echo=FALSE}
knitr::include_graphics("depends/variance-proportions.pdf")
```

>>>>

@@

```{r echo=FALSE}
knitr::include_graphics("depends/3-continental-map.png.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/aaa-variance-proportions.pdf")
```
